What is an Ancestral Recombination Graph?

### 2022-02-03 paper.tex

We describe here an alternative formulation in which the
concepts are based on the diploid pedigree, which
is free from the limitations discussed in the previous section.
\cite{mathieson2020ancestry} and others [CITE] have also
suggested this approach, although without explicitly defining
the roles of nodes and the details of how ancestry
flows along edges.

>>>>

We describe here an alternative formulation in which the
concepts are based on the diploid pedigree, which
is free from the limitations discussed in the previous section.
\cite{mathieson2020ancestry} and others 
\citep{wakeley2012genetics,gusfield2014recombinatorics,speed2015naturereviewsgenetics}
have also suggested this approach, although without explicitly defining
the roles of nodes and the details of how ancestry
flows along edges.
